Examples Compendium

### 2021-01-12 examples.tex
added explanation to first two examples

In terms of tableax the fusion $Z\ast Z'$ can be encoded as 
\begin{align}
    \young(1,2,4) \ast \young(3) &= \young(13,2,4) + \young(14,2,3) \\
    S_3 \ast (1\leftarrow 2) &= (1\leftarrow 2 \to 3) + P_3 \\ 
    (000,00,1)\ast (010,00,0) &= (010,00,1) + (001,00,0) \\
    &= (A_0 , A_5, A_1A_4 - A_2A_3) \sqcup (A_0 , A_1, A_3) 
\end{align}
where the ideals in line 3 are given in coordinates on matrices of the form
\[
    \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
        0 & A_0 & A_1 & A_2\\
        0 & 0 & A_3 & A_4\\
        0 & 0 & s & A_5\\
        0 & 0 & 0 & 0
        \end{BMAT}\right]
\]

@@

Again, in terms of tableaux, $Z\ast Z'$ is given by 
\begin{align}
    \young(2,4) \ast \young(1,3) &= \young(13,24) + \young(12,34) \\
    (1\to 2\leftarrow 3) \ast S_2 &= P_2 + (2\leftarrow 3) \oplus (1 \to 2) \\
    (100,01,0) \ast (000,10,0) &= (010,01,0) + (100,11,0) 
\end{align}

TODO: fill in the ideals.

>>>>

In terms of tableax the fusion $Z\ast Z'$ can be encoded as 
\begin{align}
    \young(1,2,4) \ast \young(3) &= \young(13,2,4) + \young(14,2,3) \\
    S_3 \ast (1\leftarrow 2) &= (1\leftarrow 2 \to 3) + P_3 \\ 
    (000,00,1)\ast (010,00,0) &= (010,00,1) + (001,00,0) \\
    &= (A_0 , A_5, A_1A_4 - A_2A_3) \sqcup (A_0 , A_1, A_3) 
\end{align}
where the ideals in line 3 are given in coordinates on matrices of the form
\[
    \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
        0 & A_0 & A_1 & A_2\\
        0 & 0 & A_3 & A_4\\
        0 & 0 & s & A_5\\
        0 & 0 & 0 & 0
        \end{BMAT}\right]
\]
Check that 
\[
\begin{gathered}
    E_0 = \{\e_1 , \e_2 , \e_4 - \frac 1 s A_5 \e_3 \} \to \{\e_1 , \e_2 , - A_5 \e_3 \} \\
    E_s = \{\e_3 + \frac 1 s A_3 \e_2 + \frac 1 s A_1 \e_1 \} \to \{A_3 \e_2 + A_1 \e_1 \}
\end{gathered}    
\]
The equations imposed by the factor tableaux also degenerate.
\[
(A_0, sA_2 - A_1 A_5, sA_4 - A_3 A_5) \to (A_0, A_1A_5, A_3A_5) = (A_0,A_5) \sqcup (A_0, A_1, A_3)
\]
Need to supplement $A_5 = 0$ case with $\col_3 \wedge \col_4 = 0$ or $A_1 A_4 - A_2 A_3 = 0$ in order that $\dim \ker A = 3$.

\begin{remark}
    If we take $s\to\infty$ in $E_0$, $E_s$ we get the spanning set $\{\e_1,\e_2,\e_4\}\sqcup\{\e_3\}$. Does this have any significance? 
\end{remark}

@@

Again, in terms of tableaux, $Z\ast Z'$ is given by 
\begin{align}
    \young(2,4) \ast \young(1,3) &= \young(13,24) + \young(12,34) \\
    (1\to 2\leftarrow 3) \ast S_2 &= P_2 + (2\leftarrow 3) \oplus (1 \to 2) \\
    (100,01,0) \ast (000,10,0) &= (010,01,0) + (100,11,0) \\
    & = (A_5, A_0) \sqcup (A_3, A_0 A_4 + A_1 A_5)
\end{align} 
% 
% TODO: fill in the ideals. 
Let's verify with MVy. Consider
\[
    A = \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
        s & A_0 & A_1 & A_2\\
        0 & 0 & A_3 & A_4\\
        0 & 0 & s & A_5\\
        0 & 0 & 0 & 0
        \end{BMAT}\right] \qquad A-s = 
        \left[\begin{BMAT}(e){c;c;c;c}{c;c;c;c} 
            0 & A_0 & A_1 & A_2\\
            0 & -s & A_3 & A_4\\
            0 & 0 & 0 & A_5\\
            0 & 0 & 0 & -s
            \end{BMAT}\right]
\]
Then 
\begin{align}
    E_0 &= \{s \e_2 - A_0 \e_1, \\
     & sA_0 \e_4 - A_0 A_5 \e_3 + A_1 A_5 \e_2 - A_0 A_1 \e_1 \text{ if } sA_4 - A_3 A_5 = 0 \}\\
     &\to \{ \e_1, -A_0A_5 \e_3 + A_1 A_5 \e_2 - A_0 A_1 \e_1 \text{ if } A_3 A_5 = 0 \} \\
    E_s &= \{\e_1, \\
        & s\e_3 + A_3 \e_2 \text{ if } sA_1 + A_0 A_3 = 0 \} \\
        &\to \{ \e_1 , \e_2 \text{ if } A_0 A_3 = 0  \}
\end{align}
From this we see that $Z\ast Z'$ is contained in
\[
(A_3 A_5 , A_0 A_3) = (A_3) \sqcup (A_5, A_0) 
\]
Expected dimension is $4 + 3 - 2 - 1 = 4$ hence the first ideal is not big enough. Indeed the case $A_3 = 0$ and $A_5 \ne 0$ has to be supplemented with $A\big|_{s=0}^2 = 0$ since the total Jordan type is $(1,1) + (1,1) = (2,2)$. This adds the condition $A_0 A_4 + A_1 A_5 = 0$.
